---
title: "R Notebook"
output: html_notebook
---
```{r}



library(tidyverse)
library(cancensus)
library(sp)
library(raster)
library(rgdal)
library(GISTools)
library(rgdal)
library(sf)

set_api_key('CensusMapper_a59bd92664838827e0a0f561a560600f', install = TRUE, overwrite = TRUE)
options(cancensus.cache_path = "/Users/shivyucel/Documents/projects.nosync/R Learning/Transport_Analyses/cache")


```

#1. Access DA census shapes across Toronto and Vancouver 
Toronto has region code 35535, Vancouver has region code 59933

```{r}
list_census_regions('CA16') %>% 
  filter(level == "CMA", name %in% c("Vancouver","Toronto"))
```

### Get Toronto DA shapes

```{r}

toronto_DA <- get_census(dataset='CA16', regions=list(CMA="35535"),
level='DA', use_cache = FALSE, geo_format = 'sf', quiet = TRUE)

```


### Get Vancouver Shape

```{r}

vancouver_DA <- get_census(dataset='CA16', regions=list(CMA="59933"),
level='DA', use_cache = FALSE, geo_format = 'sf', quiet = TRUE)

```



#1. Access CT census shapes across Toronto and Vancouver 
Toronto has region code 35535, Vancouver has region code 59933

```{r}
list_census_regions('CA16') %>% 
  filter(level == "CMA", name %in% c("Vancouver","Toronto"))
```

### Get Toronto CT shapes

```{r}

toronto_CT <- get_census(dataset='CA16', regions=list(CMA="35535"),
level='CT', use_cache = FALSE, geo_format = 'sf', quiet = TRUE)

```

```{r}
st_write(toronto_CT, "/Users/shivyucel/Documents/projects.nosync/opioid_accessibility/project/project_dir/data/toronto_data/toronto_shapes/CT_geometries/CT_shp.shp")
```

### Get Vancouver CT Shape

```{r}

vancouver_CT <- get_census(dataset='CA16', regions=list(CMA="59933"),
level='CT', use_cache = FALSE, geo_format = 'sf', quiet = TRUE)

```

```{r}
st_write(toronto_CT, "/Users/shivyucel/Documents/projects.nosync/opioid_accessibility/project/project_dir/data/toronto_data/toronto_shapes/CT_geometries/CT_shp.shp")
```































```{r}
library(tidyverse)
library(cancensus)
library(sp)
library(raster)
library(rgdal)
library(GISTools)
library(rgdal)
library(sf)

set_api_key('CensusMapper_a59bd92664838827e0a0f561a560600f', install = TRUE, overwrite = TRUE)
options(cancensus.cache_path = "/Users/shivyucel/Documents/projects.nosync/R Learning/Transport_Analyses/cache")


```

#1. Access income variables for Toronto



```{r}
variables <- list_census_vectors("CA16")
```


```{r}
# Returns a data frame with data only
census_data <- get_census(dataset='CA16', regions=list(CMA="35535"),
                          vectors=c("v_CA16_4986","v_CA16_401"),
                          level='DA', use_cache = FALSE)

```

```{r}
library(sf)
cens = st_write(census_data, "/Users/shivyucel/Documents/projects.nosync/opioid_accessibility/opioid_accessibility/data/toronto_data/census_data/DA_income.csv")

```


## Access Age Variables for Toronto


```{r}

#1. Access income variables for Toronto



```{r}
variables <- list_census_vectors("CA16")
```


```{r}
# Returns a data frame with data only
census_data <- get_census(dataset='CA16', regions=list(CMA="35535"),
                          vectors=c("v_CA16_379","v_CA16_3636"),
                          level='DA', use_cache = FALSE)

```
```{r}
library(sf)
cens = st_write(census_data, "/Users/shivyucel/Documents/projects.nosync/opioid_accessibility/opioid_accessibility/data/toronto_data/census_data/age_newcomer.csv")

```


